Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Minor corrections - removed some whitespace at eols
changed some of optimization discussion

\subsection{Optimizing results}
We have not used the fastest possible implementations possible for various
reasons mentioned previously. However, if we had actually used the fastest
implementations in \ac{SUPERCOP}, achieved median speed for every hash
calculated the results should look as in Table X. The table is calculated using
the lengths of data actually hashed by Tahoe-\ac{LAFS}, the medians from
\ac{SUPERCOP} results, and interpolation for sizes in between those mentioned in
\ac{SUPERCOP}. The point of this result is to see the maximum performance gain
possible for TAHOE-\ac{LAFS} by adopting one of the current \ac{SHA}-3
candidate implementations.

@@

The Python-bindings generated for Cython in C are not necessarily the most
optimized versions possible to write and they are ugly to read or change (from
a C perspective). However we consider them to be good enough, and they are
equal for all the \ac{SHA}-3 candidates which means they should give the same
performance penalty. The \ac{SHA}-256 version will of course not suffer from
the same penalty, however we believe the possible performance gain is small.
This is due to the fact that no intensive operations take place in our
Cython-code.

>>>>

\subsection{Optimizing results}
We have not used the fastest possible implementations possible for various
reasons mentioned previously. However, if we had actually used the fastest
implementations in \ac{SUPERCOP}, achieved median speed for every hash

@@

The Python-bindings generated for Cython in C are not necessarily the most
optimized versions possible to write and they are ugly to read or change (from
a C perspective). However we consider them to be good enough, and they are
equal for all the \ac{SHA}-3 candidates which means they should give the same
performance penalty. The \ac{SHA}-256 version will of course not suffer from
the same penalty, however we believe the possible performance gain is small.
This is due to the fact that no intensive operations take place in our
Cython-code. However we do believe that our bindings are affected by the
